Validating risk scores

### 2020-11-05 manuscript/risk_scores.Rmd

all_auc <- rbind(acp_auc, chen_liu_auc, shi_et_al_auc, caramelo_auc, bc_auc, age_auc)
compare_auc_to_orig(rbind(acp_auc_orig, chen_liu_auc_orig, shi_et_al_auc_reported_admission,
                         shi_et_al_auc_reported_all, bc_auc_orig),
                    all_auc, show_outcome = FALSE)

>>>>

all_auc <- rbind(acp_auc, chen_liu_auc, shi_et_al_auc, caramelo_auc, bc_auc, age_auc)
all_auc_orig <- rbind(acp_auc_orig, chen_liu_auc_orig, shi_et_al_auc_reported_admission,
                         shi_et_al_auc_reported_all, bc_auc_orig)

write_csv(all_auc, here::here("manuscript", "all_auc.csv"), na = "")
write_csv(all_auc_orig, here::here("manuscript", "all_auc_orig.csv"), na = "")

compare_auc_to_orig(all_auc_orig,
                    all_auc, show_outcome = FALSE)
